Demand Forecasting of individual Probability Density Functions with Machine Learning

### 2020-09-12 LaTex/paper.tex
journal submission

\author[1]{Felix Wick \thanks{felix.wick@blueyonder.com}}
\author[3]{Ulrich Kerzel \thanks{u.kerzel@iubh-fernstudium.de}}
\author[1]{Martin Hahn \thanks{martin.hahn@blueyonder.com}}
\author[1]{Moritz Wolf \thanks{martin.hahn@blueyonder.com}}
\author[2]{Trapti Singhal \thanks{trapti.singhal@blueyonder.com}}
\author[1]{Michael Feindt \thanks{michael.feindt@blueyonder.com}}
\affil[1]{\small Blue Yonder GmbH (Ohiostra{\ss}e 8, 76149 Karlsruhe, Germany)}
\affil[2]{\small Blue Yonder India Private Limited (Bengaluru, India)}
\affil[3]{\small IUBH Internationale Hochschule (Erfurt, Germany)}

@@

\noindent
While the Poisson histogram shows a clear pattern of too narrow PDF predictions (see \fig \ref{fig:cdf_histos}), the most significant deviations of the negative binomial histogram from the uniform distribution can be found in the first bins of CDF values close to $0$ (overprediction) as well as in the last bins of CDF values close to $1$ (underprediction). The first case is mainly due to a slight zero inflation of actual sales. The latter case primarily stems from slow moving articles with less than one item sold per store per day on average, what can be seen in plots c and d of \fig \ref{fig:cdf_demand}, where the spike at CDF values close to $1$ is reduced by excluding all samples with mean predictions lower than $1.0$. The resulting distribution for the negative binomial model indicates a slight tendency towards too broad PDF predictions, at least for some observations.

@@

\fig \ref{fig:invquant_mean} shows the inverse quantile profile plot using the predicted mean as the $x$-axis of the graph, meaning that the distributions are grouped such that the 15 columns correspond to mean predictions in 12 intervals with widths of 5 from 0.0 to 60.0 and 3 remaining intervals $[60.0, 70.0]$, $(70.0, 80.0]$, and $(80.0, 100.0]$ (with mean predictions higher than 100.0 included in the highest interval), while we aggregate over all locations, items, and sales dates. The considered quantiles are chosen to be the same as in \fig \ref{fig:invquant_dayofweek}. While the Poisson model again shows a significant pattern of too narrow PDF predictions across the full range of mean prediction values, we can also see several deviations from the expected uniform behavior for the negative binomial model. For mean predictions around $30$, the negative binomial model deviates significantly from the expected behavior, with the shape of the deviations pointing towards too broad PDF predictions (as also observed in the CDF histogram above). And for mean predictions higher than $80$, the pattern of the deviations indicate an underprediction of the mean parameter. The deviations at very low predicted mean values reflect the complications of slow-sellers described in the context of CDF histograms above.

>>>>

\author[1]{Felix Wick \thanks{felix.wick@blueyonder.com}}
\author[3]{Ulrich Kerzel \thanks{u.kerzel@iubh-fernstudium.de}}
\author[1]{Martin Hahn \thanks{martin.hahn@blueyonder.com}}
\author[1]{Moritz Wolf \thanks{moritz.wolf@blueyonder.com}}
\author[2]{Trapti Singhal \thanks{trapti.singhal@blueyonder.com}}
\author[1]{Michael Feindt \thanks{michael.feindt@blueyonder.com}}
\affil[1]{\small Blue Yonder GmbH (Ohiostra{\ss}e 8, 76149 Karlsruhe, Germany)}
\affil[2]{\small Blue Yonder India Private Limited (Bengaluru, India)}
\affil[3]{\small IUBH Internationale Hochschule (Erfurt, Germany)}

@@

\noindent
While the Poisson histogram shows a clear pattern of too narrow PDF predictions (see \fig \ref{fig:cdf_histos}), the most significant deviations of the negative binomial histogram from the uniform distribution can be found in the first bins of CDF values close to $0$ (overprediction) as well as in the last bins of CDF values close to $1$ (underprediction). The first case is mainly due to a slight zero-inflation of actual sales. The latter case primarily stems from slow moving articles with less than one item sold per store per day on average, what can be seen in plots c and d of \fig \ref{fig:cdf_demand}, where the spike at CDF values close to $1$ is reduced by excluding all samples with mean predictions lower than $1.0$. The resulting distribution for the negative binomial model indicates a slight tendency towards too broad PDF predictions, at least for some observations.

@@

\fig \ref{fig:invquant_mean} shows the inverse quantile profile plot using the predicted mean as the $x$-axis of the graph, meaning that the distributions are grouped such that the 15 columns correspond to mean predictions in 12 intervals with widths of 5 from 0.0 to 60.0 and 3 remaining intervals $[60.0, 70.0]$, $(70.0, 80.0]$, and $(80.0, 100.0]$ (with mean predictions higher than 100.0 included in the highest interval), while we aggregate over all locations, items, and sales dates. The considered quantiles are chosen to be the same as in \fig \ref{fig:invquant_dayofweek}. While the Poisson model again shows a significant pattern of too narrow PDF predictions across the full range of mean prediction values, we can also see several deviations from the expected uniform behavior for the negative binomial model. For mean predictions around $30$, the negative binomial model deviates significantly from the expected behavior, with the shape of the deviations pointing towards too broad PDF predictions (as also observed in the CDF histogram above). And for mean predictions higher than $80$, the pattern of the deviations indicate an underprediction of the mean parameter. The deviations at very low predicted mean values reflect the complications of zero-inflation and slow-sellers seen in the first and last bins of the CDF histograms above.
